A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-08-25 bioc-workflow.Rmd
minor changes

```{r readMSnSet2}
hl <- readMSnSet2(csvfile, ecol = c(8:27), fnames = 1, skip = 1)
```

@@

To list all data distributed with a package, one can use pass the
package name as input to the `data` function. For instance

```{r pkgdata, eval=FALSE}
data(package = "pRolocdata")
```

will list the `r nrow(data(package = "pRolocdata")$results)` datasets
that are available in `r Biocexptpkg("pRolocdata")`.

>>>>

```{r readMSnSet2}
hl <- readMSnSet2(csvfile, ecol = 8:27, fnames = 1, skip = 1)
```

@@

To list all data distributed with a package, one can use use the
`pRolocdata` function.

```{r pkgdata, eval=FALSE}
pRolocdata()
```

will list the `r nrow(pRolocdata()$results)` datasets
that are available in `r Biocexptpkg("pRolocdata")`.
